\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-20 paper/main.tex
.

The results of this analysis are summarized in part (c) of Table \ref{tab:Results}, calculating the performance of all considered methods over their original splitting scheme and over a protein split. We find that, first the majority of approaches evaluate over a drug--protein splitting scheme, while second, the highest performances on Yamanishi dataset are yielded over the drug--target pairs splitting scheme, with a noticeable gap to the methods performing their splits over proteins. Further, when evaluating the same methods over a protein split, we find a substantial performance divergence in comparison to their original splitting scheme. The authors of DTI-CDF evaluate their method on all three splitting schemes underlining this point. While \name provides comparable performance to DTI-CDF, it yields considerably better with respect to $MicroAUC_p$.

>>>>

The results of our experiments are summarized in part (c) of Table
\ref{tab:Results}; we calculated the performance of all compared
methods over their original splitting scheme and over a protein
split. First, we find that there is a large difference in performance
when evaluating over a drug--target pair split compared to a
protein split, with generally higher performance achieved when using
the drug--target pair split.
Second, when evaluating the same methods over a protein split, we find
a substantial performance difference in comparison to the splitting
scheme used in the original evaluation of each method. DTI-CDF was
originally evaluated on all three splitting schemes underlining this
point \cite{}. While \name provides comparable performance to DTI-CDF,
it yields considerably better results with respect to $MicroAUC_p$.
